Kaggle-in-class Data Challenges Can Boost Student Learning

### 2019-09-03 paper-kaggle.Rmd
final changes to address reviwers comments + move figure4

Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam. This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee. The data from this survey was viewed by the researchers after all course grades had been reported.

@@

>>>>

Students in MAST90083 and ETC5242 were invited to give feedback about the course, in particular about the data competitions, before the final exam. This information was voluntary, and students who completed the questionnaire were rewarded with a coupon for a free coffee. The data from this survey was viewed by the researchers after all course grades had been reported. To reduce potential bias in students replies, we emphasize this point as part of the instruction at the beginning of the survey.

@@

# Future work

This work is one of a few quantitative analyses of data competition influences on students' performance. More evidence needs to be collected from other STEM courses to demonstrate consistent positive influence. Moreover, future investigation is required to understand the influence of the different aspects of data competition implementation on the magnitude of the performance improvement. For example, the competition duration, availability and accessibility of additional material, requirement of writing a final report or giving a short oral presentation are elements worth investigating. In this work we couldn't provide statistically significant evidence for positive influence of the data competition on the engagement and the interest. This should be addressed in a future work. Finally, it will be interesting to investigate if some sub-group of students benefits more from proposed competitions, e.g. undergraduate vs graduate students or female vs male students.
